### 2018-08-05 paper/design.tex
added all I could do easily on the system's design

\section{Design of the \name file transfer system}%
\label{design}
\sonja{will frame and structure (A) squad overlay (prediction) (B)
  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
  if not included earlier (F) out-of-band}
\commentDaniel{I suggest the following structure:
  (A) Sphinxes
  (B) SPOR (global overlay)
  (C) SPORES (local overlay).
  My original idea was to make Sphinxes its own section before the design 
  section instead of a subsection in the design section.}
\sonja{remove/update references to building blocks, POR}
\commentDaniel{I removed the building blocks subsection entirely.}

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and 
\changeAL{routing information that they will use to transfer the file's content over \name's network of unreliable nodes.}
%use-once reply mix-headers.
%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline.pdf_tex}
  \caption{\label{fig:outline}%
    %\commentDaniel{We must adapt this figure to the text.}%
    Outline of \name's components. Users squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them to random peers (\cref{sec:SPOR}); using the two above 
    overlays allows for the creation of \ac{SPOR} between sets of devices. 
    These protocols enables secure file transfer between users 
    (\cref{SPORES}).}
\end{figure}

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    describes the characteristics of the \changeAL{network nodes}, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}

@@

\include*{sphinxes}
\include*{spor}
\commentAL{What I want to do from here:
(1) The squad overlay, where a user's devices exchange behavioral information;
(2) Predicting a device's availability;
(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
(4) File exchange.}
\include*{squad-overlay-design}
\include*{file-transfer-design}

>>>>

\section{Design of the \name file transfer system}%
\label{design}
\sonja{will frame and structure (A) squad overlay (prediction) (B)
  global overlay (RPS) (C) sphinxes (incl.\ sphinx, onion routing in
  general) (D) SPOR and SPORES (E) encryption (hybrid, payload, header)
  if not included earlier (F) out-of-band}
\commentDaniel{I suggest the following structure:
  (A) Sphinxes
  (B) SPOR (global overlay)
  (C) SPORES (local overlay).
  My original idea was to make Sphinxes its own section before the design 
  section instead of a subsection in the design section.}

Our goal is to enable private and reliable file exchange between users 
participating in the system, by using their respective devices only.
When Alice and Bob, two users of our system, want to exchange a file \(f\) 
through \name; they start by sharing some information out-of-band, \eg from 
their smartphones.
More precisely, they exchange metadata on \(f\), encryption keys, and 
\changeAL{routing information that they will use to transfer the
  file's content over \name's network of unreliable nodes.}
\sonja{here comes more of a solution overview and reference to the outline
  figure.}

Figure \cref{fig:outline} shows the components needed to obtain this
routing information.  
%use-once reply mix-headers.
%They use these reply headers to transfer the file contents of \(f\) over a network of unreliable nodes while also achieving privacy.

\begin{figure}[t]
  \centering
  \def\svgwidth{0.8\columnwidth}
  \import{figures/}{outline.pdf_tex}
  \caption{\label{fig:outline}%
    %\commentDaniel{We must adapt this figure to the text.}%
    Outline of \name's components. Users' squads of devices are circled in gray. 
    From top to bottom: a user's devices collaborate through the Squad Overlay 
    (\cref{sec:squad_overlay}); online devices globally share information about 
    them with random peers (\cref{sec:SPOR}); using the two 
    overlays above allows for the creation of routes (\ac{SPOR}) between sets of devices. 
    These protocols enable secure file transfer between users 
    (\cref{sec:sphinxes}).}
\end{figure}

After the initial, out-of-band setup, file transfer happens along
onion routes but with the following \name modifications:

\sonja{might need different naming, and deciding about predictive and probabilistic}
\begin{description}
\item [Stateless.] There is no mandatory circuit creation, the file transfer can be
  done in a stateless way. 
\item [Predictive.] The choice of nodes included in the onion routing
  layers is based on a predictive model for availability, disseminated
  according to Figure~\cref{fig:outline}, and queried by random peer sampling.
\item [Probabilistic.] Instead of source routes with one node per onion layer, each
  layer consists of a set of nodes and although the source route still
  determines the sequence of layers, the actual node used for the next
  hop of forwarding is selected from the set in an ad-hoc way.
\end{description}

This rest of this section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They classify anonymous communication protocols using the following 
categories (see~\cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    describes the characteristics of the \changeAL{network nodes}, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization);
    \end{enumerate*}

@@

\include*{sphinxes}
\include*{spor}
\commentAL{What I want to do from here:
(1) The squad overlay, where a user's devices exchange behavioral information;
(2) Predicting a device's availability;
(3) What is at the moment III-B SPOR: global overlay (one-liner: ``we use a RPS service'') and nodes selection per layer etc.;
(4) File exchange.}
\include*{squad-overlay-design}
%\include*{file-transfer-design}
